Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-30 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Ehsan: move graph to the right section
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4570 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

%   - Delay vs % wires cut & wire delay
\subsection{Circuit Speed vs. Interposer Delay}
To investigate the impact of the interposer delay (\textit{delay increase}), we keep all other interposer parameters constant and sweep the \textit{delay increase} from 0 to 1.5 \textit{ns}. We use \textit{number of cuts} $= 1$ (i.e. two dice), \textit{bidirectional interposer wires = on}, \textit{fanin transfer = on}, and \textit{fanout transfer = on}.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{delays_crit_path_new.eps}
\caption{Critical path delay vs. \textit{\% wires cut} for 2 dice and $0.0$, $0.5$, $1.0$ and $1.5ns$ of \textit{delay increase}.}
\label{fig:delays_crit}
\end{figure}

>>>>

%   - Delay vs % wires cut & wire delay
\subsection{Circuit Speed vs. Interposer Delay}

\begin{figure}[!b]
\centering
\includegraphics[width=\linewidth]{delays_crit_path_new.eps}
\caption{Critical path delay vs. \textit{\% wires cut} for 2 dice and $0.0$, $0.5$, $1.0$ and $1.5ns$ of \textit{delay increase}.}
\label{fig:delays_crit}
\end{figure}

To investigate the impact of the interposer delay (\textit{delay increase}), we keep all other interposer parameters constant and sweep the \textit{delay increase} from 0 to 1.5 \textit{ns}. We use \textit{number of cuts} $= 1$ (i.e. two dice), \textit{bidirectional interposer wires = on}, \textit{fanin transfer = on}, and \textit{fanout transfer = on}.

@@
